---
title: "Assignment5"
author: "Anand R"
date: "September 30, 2018"
output: 
   html_document:
      keep_md: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown

Doing Data Science - Tidy Data
Live session Unit 05 assignment

Question 1: 
<!--The client expects a baby soon , for which we need to select names from a repository of names. The raw data is provided.
The file is yob2016.txt with children born in 2016 in US.
Consist of Firstname Gender and number of children count with the name.
-->

```{r echo = TRUE}
childNames <- read.delim("C:/Anands/DS_HW/yob2016.txt",header = FALSE, sep = ";")
head(childNames)
# assign the child names to a data frame.
cndf <- data.frame(childNames)

colnames(cndf)<- c("first_name","gender","amount_of_children")

fn <- grep("y{3}" , cndf$first_name)

stri <- c(grep("yyy", cndf$first_name , value = TRUE))

stri

y2016 <- cndf[-grep("y{3}" , cndf$first_name),] 

delf <- grep("y{3}" , y2016$first_name)

head(delf) 
# the record has been deleted

#To create csv file y2016.csv in the data directory for github

write.table(y2016, "/Anands/DS_HW/GIT/DS_HomeWork/Data/y2016.csv", sep = ",", row.names = FALSE)

```
<!--End of part 1 -->

#Data Merging  - Part 2

<!-- Utilize the file yob2015.txt to import to a dataframe and try to merge the file with the earlier file.
The final file will not have any NA values in the amount of children rows.
-->
```{r echo = TRUE}
childNames2 <- read.delim("C:/Anands/DS_HW/yob2015.txt",header = FALSE, sep = ",")

#Display last 10 rows.
tail(childNames2,10)

# assign the child names to a data frame.
y2015 <- data.frame(childNames2)

colnames(y2015)<- c("first_name","gender","amount_of_children2")

final <- merge(y2016, y2015, by=c("first_name"))

```
#interesting facts on the last ten rows in y2015.
Interesting fact about these 10 tail rows are
1. All of them start with 'Z'.
2. All are males by gender
3. All of them have amount of children as 5 nos.

#Data Summary
Add amount of 2015 and 2016 (amount of children) together and sort data to show top 10 popular girl names from the two years combined.

```{r}
# Creating new column
final$Total <- NA
# Count total and asssign to Total
final$Total <- c(final$amount_of_children + final$amount_of_children2)

# sort data by top counts
final <- dplyr::arrange(final, desc(final$Total))

top10 <- head(final,10)

# people given top 10 popular names
totl <- sum(top10$Total)

totl # this gives total number of popular names in two years.

fgirl <- subset(x=final, final$gender.x=='F' & final$gender.y =='F' )

#Arrange top 10 girls in the final girls data frame

fgirl <- dplyr::arrange(fgirl, desc(fgirl$Total))

top10girls <- head(fgirl,10)

csvdf <- data.frame(top10girls$first_name, top10girls$Total)

colnames(csvdf)<- c("first_name","Total")

csvdf

#To create csv file top10girl_names.csv in the data directory for github

write.table(csvdf, "/Anands/DS_HW/GIT/DS_HomeWork/Data/top10girl_names.csv", sep = ",", row.names = FALSE)

```

#The CodeBook on assignment 5

* Created on 9/30/2018 by Anand Rajan

<!--
a.	GitHub for your SMU MSDS homework.  

The homework assignment 5 is created two files in the local GIT directory
#Created in /Anands/DS_HW/GIT/DS_HomeWork in GIT local.
*This project is created to handle the Data science collaborative work between cohorts of Fall 2018 class.

Also created the output data files in /Anands/DS_HW/GIT/DS_HomeWork/Data
and the RMarkdown files in /Anands/DS_HW/GIT/DS_HomeWork/RMarkdown directory path.
-->

#Data munging:

<!--
The data is read in to data frame from yob2016.txt
assigned the child names to a data frame.
assigned column names to the data.

Identify the data that had the 'yyy' to ther first name.
display the name with 'yyy' at the end.

Eliminate the rwo as it was a duplicate row after cleansing.
The record has been deleted

To create csv file y2016.csv in the data directory for github
write.table was used.
-->

#Merging

Read another csv file yob2015 for merge.

Merged 2015 and 2016 files together.



#Data Summary

* Creted new column "Total" in the temple.

The final dataframe has first_name, gender and amount of children from each data set. and create the total.

Sorted the data by desc total.

Created a list of top 10 names from 2015 and 2016.

Omit boy names from the list to create top 10 girl names.

* Created in /Anands/DS_HW/GIT/DS_HomeWork in GIT local.


Also created the output data files in /Anands/DS_HW/GIT/DS_HomeWork/Data
and the RMarkdown files in /Anands/DS_HW/GIT/DS_HomeWork/RMarkdown directory path.


#Files Location information

location of data files in 

* https://github.com/AnandRHUB/DS_HomeWork/Data

Location of rmd and html files are in 

* https://github.com/AnandRHUB/DS_HomeWork/RMarkdown

The Rmarkdown is in https://github.com/AnandRHUB/DS_HomeWork/RMarkdown/Assignment5.rmd

The matching html is in https://github.com/AnandRHUB/DS_HomeWork/RMarkdown/Assignment5.html


The data files y2016 consist of baby names born in US for the year 2016.
The columns of interest are first_name, gender and amount of children.

The data file for 2015 was merged with this file to get the final output for two years.

The final data set stored in 

The second data file is a set of top 10 girl in

* /Anands/DS_HW/GIT/DS_HomeWork/Data/top10girl_names.csv

This file contains data about top 10 girl names chosen between 2015 and 2016 for the client's benefit as the client is expecting  girl baby this year.

#The End
